Using Monte Carlo Renormalization Group (MCRG) to study the Ising model on a two dimensional square lattice

### 2019-03-15 PaperDraft.tex
save to data/directory
removed intermediate files from latex
data analysis
add to paper data with error, remove redundant stuff
size 32 error analysis

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage[overload]{empheq}
\usepackage{float}
\usepackage{graphicx}
\usepackage{indentfirst}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|} 
 \hline
 Lattice linear dimension $L$ & 64 & 32 & 16 & 8 \\ 
 \hline
 \# of burn-in steps $N_{warm}$ & $2\times 10^4$& $1\times 10^4$& $0.5\times 10^4$& $0.2\times 10^4$ \\ 
 \hline
 \# of measurement steps $N_{meas}$& $50\times 10^4$& $40\times 10^4$& $20\times 10^4$& $10\times 10^4$\\
 \hline
 \# of MC steps between measurements $\Delta_N$ & 10 & 8 & 5 & 5 \\
 \hline
 \# of samples $N_{data} = N_{meas}/\Delta_{N}$ & $5\times 10^4$& $5\times 10^4$& $4\times 10^4$& $2\times 10^4$ \\
 \hline
 \end{tabular}
 \caption{\label{MCSettings}Monte Carlo simulation settings}
\end{table}

@@

\section{Results}
All results for $y_T$ are shown in Table ~\ref{yT} below.
\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|c|} 
\hline
 \multicolumn{2}{|c|}{ }& \multicolumn{4}{c|}{Lattice size L}\\
 \hline
 $n$ & $N_c$ & 64 & 32 & 16 & 8 \\
 \hline
 1 & 1 & & 0.90788777& 0.89635236 & 0.88213852\\
 1 & 2 & & 0.9656497 & 0.96172657 & 0.95997822\\
 1 & 3 & & 0.96821987& 0.96560534 & 0.96333859\\
 1 & 4 & & 0.96974414 & 0.96185282 & 0.95932521\\
 1 & 5 & & 0.96872342 & 0.96075818 & 0.96106577\\
 1 & 6 & & 0.96883716 & 0.96134885 & 0.96105902\\
 1 & 7 & & 0.96684275 & 0.96791929 & 0.96185279\\
 \hline
 2 & 1 & & & & 0.88213852\\
 2 & 2 & & & & 0.95997822\\
 2 & 3 & & & & 0.96333859\\
 2 & 4 & & & & 0.95932521\\
 2 & 5 & & & & 0.96106577\\
 2 & 6 & & & & 0.96105902\\
 2 & 7 & & & & 0.96185279\\
 \hline
 3 & 1 & & & & 0.88213852\\
 3 & 2 & & & & 0.95997822\\
 3 & 3 & & & & 0.96333859\\
 3 & 4 & & & & 0.95932521\\
 3 & 5 & & & & 0.96106577\\
 3 & 6 & & & & 0.96105902\\
 3 & 7 & & & & 0.96185279\\
 \hline
 \end{tabular}
 \caption{\label{yT}thermal eigenvalue
exponent $y_T$ as a function of the number of RG iterations $N_r$, the number of coupling
constants in the RG analysis $N_c$}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|c|} 
\hline
 \multicolumn{2}{|c|}{ }& \multicolumn{4}{c|}{Lattice size L}\\
 \hline
 $n$ & $N_c$ & 64 & 32 & 16 & 8 \\
 \hline
 1 & 1 & & 1.88090467 & 1.8793387 & 1.87620229\\
 1 & 2 & & 1.88051803 & 1.87969459 & 1.8788031\\
 1 & 3 & & 1.88052089 & 1.87973553 & 1.87884904\\
 1 & 4 & & 1.88090765 & 1.88016303 & 1.87917633\\
 \hline
 2 & 1 & & & & \\
 2 & 2 & & & & 0.95997822\\
 2 & 3 & & & & 0.96333859\\
 2 & 4 & & & & 0.95932521\\
 \hline
 3 & 1 & & & & 0.88213852\\
 3 & 2 & & & & 0.95997822\\
 3 & 3 & & & & 0.96333859\\
 3 & 4 & & & & 0.95932521\\
 \hline
 \end{tabular}
 \caption{\label{yH}thermal eigenvalue
exponent $y_T$ as a function of the number of RG iterations $N_r$, the number of coupling
constants in the RG analysis $N_c$}
\end{table}

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage[overload]{empheq}
\usepackage{float}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{listings}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|} 
 \hline
 Lattice linear dimension $L$ & 64 & 32 & 16 & 8 \\ 
 \hline
 \# of burn-in steps $N_{warm}$ & $1\times 10^4$& $1\times 10^4$& $0.5\times 10^4$& $0.5\times 10^4$ \\ 
 \hline
 \# of measurement steps $N_{meas}$& $300\times 10^4$& $150\times 10^4$& $150\times 10^4$& $150\times 10^4$\\
 \hline
 \# of MC steps between measurements $\Delta_N$ & 20 & 10 & 10 & 10 \\
 \hline
 \# of samples $N_{data} = N_{meas}/\Delta_{N}$ & $15\times 10^4$& $15 \times 10^4$& $15\times 10^4$& $15\times 10^4$ \\
 \hline
 \end{tabular}
 \caption{\label{MCSettings}Monte Carlo simulation settings}
\end{table}

@@

\section{Results}
All results for $y_T$ are shown in Table~\ref{yT} below. Uncertainties are obtained via averaging exponent values obtained over 5 independently seeded Monte Carlo runs.
\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|c|} 
\hline
 \multicolumn{2}{|c|}{ }& \multicolumn{4}{c|}{Lattice size L}\\
 \hline
 $n$ & $N_c$ & 64 & 32 & 16 & 8 \\
 \hline
 1 & 1 & & 0.902(1)& 0.899(2) & 0.884(2)\\
 1 & 2 & & 0.963(1) & 0.968(2)& 0.959(2)\\
 1 & 3 & & 0.965(2)& 0.969(1) & 0.960(3)\\
 1 & 4 & & 0.966(3) & 0.968(2) & 0.960(4)\\
 1 & 5 & & 0.965(3) & 0.967(2) & 0.955(6)\\
 1 & 6 & & 0.966(3) & 0.968(2) & 0.955(6)\\
 1 & 7 & & 0.965(3) & 0.967(3) & 0.952(5)\\
 \hline
 2 & 1 & & & & 0.88213852\\
 2 & 2 & & & & 0.95997822\\
 2 & 3 & & & & 0.96333859\\
 2 & 4 & & & & 0.95932521\\
 2 & 5 & & & & 0.96106577\\
 2 & 6 & & & & 0.96105902\\
 2 & 7 & & & & 0.96185279\\
 \hline
 3 & 1 & & & & 0.88213852\\
 3 & 2 & & & & 0.95997822\\
 3 & 3 & & & & 0.96333859\\
 3 & 4 & & & & 0.95932521\\
 3 & 5 & & & & 0.96106577\\
 3 & 6 & & & & 0.96105902\\
 3 & 7 & & & & 0.96185279\\
 \hline
 \end{tabular}
 \caption{\label{yT}thermal eigenvalue
exponent $y_T$ as a function of the number of RG iterations $N_r$, the number of coupling
constants in the RG analysis $N_c$}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|c|c|} 
\hline
 \multicolumn{2}{|c|}{ }& \multicolumn{4}{c|}{Lattice size L}\\
 \hline
 $n$ & $N_c$ & 64 & 32 & 16 & 8 \\
 \hline
 1 & 1 & & 1.8807(1) & 1.8795(2) & 1.8766(6) \\
 1 & 2 & & 1.8803(1) & 1.8800(2) & 1.8793(6)\\
 1 & 3 & & 1.8803(1) & 1.8800(3) & 1.8793(6)\\
 1 & 4 & & 1.8806(1) & 1.8804(3) & 1.8798(6)\\
 \hline
 2 & 1 & & & & \\
 2 & 2 & & & & 0.95997822\\
 2 & 3 & & & & 0.96333859\\
 2 & 4 & & & & 0.95932521\\
 \hline
 3 & 1 & & & & 0.88213852\\
 3 & 2 & & & & 0.95997822\\
 3 & 3 & & & & 0.96333859\\
 3 & 4 & & & & 0.95932521\\
 \hline
 \end{tabular}
 \caption{\label{yH}thermal eigenvalue
exponent $y_T$ as a function of the number of RG iterations $N_r$, the number of coupling
constants in the RG analysis $N_c$}
\end{table}

@@

\appendix

\section*{Appendix: My Code}
\lstinputlisting[language=Python]{"MCRG with Cluster MC - Working Version.py"}

\iffalse

\inputminted[]{python}{"MCRG with Cluster MC - Working Version.py"}
\fi
